D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-01 ootavacuous.tex
Add "as if" qualifier to excluded atomic behavior
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Prior work defines ``OOTA cycle'' by example, without a precise
definition.
Sometimes ``causal cycle'' is used as if it was a definition, but
without a clear decision process for what does and does not
constitute a causal cycle..
P0442R0 defines an OOTA cycle as a fixed-point computation that is
destroyed by perturbations, which makes perfect sense to that paper's
authors, but has left others unsatisfied.

@@

Although non-volatile accesses to atomic objects are not observable behavior,
they are still subject to the memory model.
In particular, implementations cannot:

\begin{enumerate}
\item	Invent atomic stores.
\item	Duplicate atomic stores.
\end{enumerate}

>>>>

Prior work defines ``OOTA cycle'' by example, without a precise
definition.
Sometimes ``causal cycle'' is used as if it was a definition, but
without a clear decision process for what does and does not
constitute a causal cycle.
P0442R0 defines an OOTA cycle as a fixed-point computation that is
destroyed by perturbations, which makes perfect sense to that paper's
authors, but has left others unsatisfied.

@@

Although non-volatile accesses to atomic objects are not observable behavior,
they are still subject to the memory model.
In particular, implementations must not behave as if they have:

\begin{enumerate}
\item	Invented atomic stores.
\item	Duplicated atomic stores.
\end{enumerate}
